Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
more conclusion

It is also possible that many of the nuclei from the \citet{Miller+15}
sample are not accreting in a steady fashion.  The ADAF efficiency
assumed in the right panel of Figure \ref{fig:miller} in some ways
represents the maximum value, since it does not take into account
outflows from the accretion flow that would suppress the accreiton
rate reaching large radii.  Nevertheless, many lower black hole masses
of $M_{\bullet} \lesssim 10^{8}M_{\odot}$ show X-ray luminosities lie
well above the predicted average value for stable accretion (black
line), suggesting that these galaxies either experience lower levels
of heating than average galaxies of their mass, or that they are not
accreting stably at all ($\S\ref{sec:cycle}$).  Indeed, for the lowest
mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$
exceeds the one corresponding to the maximum thermally-stable
accretion rate, $\dot{M}_{\rm TI}$ (yellow line).  Many of the upper
limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
separate ``thermally stable".  This possible dichotomy calls into
question the use of simple extrapolations of power-law fits to the
$L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
constrain the occupation fraction of black holes in low mass galaxies
(\citealt{Miller+15}).

@@

Low-mass SMBHs in the local universe ($M_{\bullet} \lesssim 3\times
10^{7}M_{\odot}$) are observed to be growing on a timescale comparable
to the age of the universe, while the most massive SMBHs with
$M_{\bullet} \gtrsim 10^{9}M_{\odot}$ possess local growth times which
are more than 2 orders of magnitude longer (\citealt{Heckman+04};
\citealt{Kauffmann&Heckman09}).

@@

    Alternatively 
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they generally to
    a factor of a few. In our model the accretion rate is determined
    from the gas properties at the stagnation radius, $\rs$, which
    agrees with the Bondi radius, $\rb$, within a factor of a
    few. Thus, use of the Bondi formula is a good approximation.
  \end{enumerate}

>>>>

It is also possible that many of the nuclei from the \citet{Miller+15}
sample are not accreting in a steady fashion.  The ADAF efficiency
assumed in the right panel of Figure \ref{fig:miller} in some ways
represents the maximum value, since it does not take into account
outflows from the accretion flow that would suppress the accreiton
rate reaching large radii.  Nevertheless, many lower black hole masses
of $M_{\bullet} \lesssim 10^{8}M_{\odot}$ show X-ray luminosities lie
well above the predicted average value for stable accretion (black
line), suggesting that these galaxies either experience lower levels
of heating than average galaxies of their mass, or that they are not
accreting stably at all ($\S\ref{sec:cycle}$).  Indeed, for the lowest
mass holes, $M_{\bullet} \lesssim 10^{8}M_{\odot}$, $L_{\rm X}$
exceeds the one corresponding to the maximum thermally-stable
accretion rate, $\dot{M}_{\rm TI}$ (yellow line).  Many of the upper
limits on $L_{\rm X}$ at low $M_{\bullet}$ may in fact correspond to a
separate ``thermally stable" population.  This possible dichotomy
calls into question the use of simple extrapolations of power-law fits
to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to
constrain the occupation fraction of black holes in low mass galaxies
(\citealt{Miller+15}).

@@

Low-mass AGN in the local universe ($M_{\bullet} \lesssim 3\times
10^{7}M_{\odot}$) are observed to be growing on a timescale comparable
to the age of the universe, while the most massive SMBHs with
$M_{\bullet} \gtrsim 10^{9}M_{\odot}$ possess local growth times which
are more than 2 orders of magnitude longer (\citealt{Heckman+04};
\citealt{Kauffmann&Heckman09}).

@@

    It is also possible that many of the galaxies in the
    \citet{Miller+15} are accreting in a non-steady fashion and this
    scatter arises from cyclic variation in accretion rate. In fact it
    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
    \Msun$ coexists with a population of smaller, steadily accreting
    black holes (e.g. the upper limits in \citet{Miller+15}.  This
    calls into question the use of simple extrapolations of power-law
    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
    to constrain the occupation fraction of black holes in low mass
    galaxies (\citealt{Miller+15}).
  \item Low mass AGN have growth times comparable to the Hubble
    time. We have show that this would require accretion rates not
    consistent with steady state thermally stable accretion of stellar
    wind material.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they generally to
    a factor of a few. In our model the accretion rate is determined
    from the gas properties at the stagnation radius, $\rs$, which
    agrees with the Bondi radius, $\rb$, within a factor of a
    few. Thus, use of the Bondi formula is a good approximation.
  \end{enumerate}
